\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{xurl}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\interfootnotelinepenalty=0

\begin{document}

\lstset{
    language=Java,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{orange},
    frame=none,
    breaklines=true,
    tabsize=2
    linewidth=\linewidth
}

\title{
    Performance Comparison of a new and already existing Approaches to Access Structures in Java
    %*\\
    %{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}
    %\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{
    \IEEEauthorblockN{
        1\textsuperscript{st} Linus Andera
    }
    \IEEEauthorblockA{
        \textit{Faculty Computer Science} \\
        \textit{Hochschule Coburg}\\
        Coburg, Germany \\
        linus.andera@stud.hs-coburg.de
    }
}

\maketitle

\begin{abstract}
    \input{sections/abstract}
\end{abstract}

\begin{IEEEkeywords}
java, native access, structure, jmh, performance, lwjgl, jna, ffma
\end{IEEEkeywords}

\section{Introduction}\label{sec:introduction}
    \input{sections/introduction}

\section{LUtils}\label{sec:lutils}
    \input{sections/lutils}

\section{Methodology}\label{sec:method}
    \input{sections/method}

\section{Results and Discussion}\label{sec:results}
    \input{sections/experiments}

\section*{Summary}
    \input{sections/summary}

%! suppress = LineBreak
\begin{thebibliography}{00}
    \bibitem{b1} S. Liang, ``The Java native interface: programmer's guide and specification,'' Addison-Wesley Professional, 1999.
    \bibitem{b2} A. Leonard, ``Java Coding Problems: Become an expert Java programmer by solving over 250 brand-new, modern, real-world problems,'' Packt Publishing Ltd, 2024.
    \bibitem{b3} F. Li, et al. ``Improving memory performance of embedded Java applications by dynamic layout modifications,'' in 18th International Parallel and Distributed Processing Symposium, IEEE Proceedings, 2004.
    \bibitem{b4} G. Tan, et al. ``Safe Java Native Interface,'' in ISSSE, 2006.
    \bibitem{b5} M. Grichi, et al. ``State of practices of java native interface,'' in Proceedings of the 29th Annual International Conference on Computer Science and Software Engineering, 2019.
    \bibitem{b6} G. Tan and J. Croft, ``An Empirical Security Study of the Native Code in the JDK,'' in Usenix Security Symposium. 2008.
    \bibitem{b7} N. Tomilov and V P. Turov, ``Evaluating the performance of Java Vector API in vector embedding operations,'' in Computing Telecommunication and Control vol. 17 issue 4, pp.7-15, 2024.
    \bibitem{b8} V. Sochat and T. Haines, ``Binary-level Software Compatibility Tool Agreement,'' arXiv preprint, arXiv:2212.03364, 2022.
    \bibitem{b9} N. Seppälä, ``Improving Java Performance With Native Libraries,'' bachelor thesis at Metropolia University of Applied Sciences, 2024.
    \bibitem{benchmark_pitfalls_1} R. Marcelino, B. Combemale, and B. Baudry, ``Automatic microbenchmark generation to prevent dead code elimination and constant folding,'' in Proceedings of the 31st IEEE/ACM International Conference on Automated Software Engineering, 2016.
    \bibitem{benchmark_pitfalls_2} H. Karer and P. Soni, ``Dead code elimination technique in eclipse compiler for Java,'' in International Conference on Control, Instrumentation, Communication and Computational Technologies (ICCICCT), IEEE, 2015.
    \bibitem{optimizing_java} B. J. Evans, J. Gough, and C. Newland, ``Optimizing Java: practical techniques for improving JVM application performance,'' O'Reilly Media Inc., 2018.
    \bibitem{disable_cpu_features} L. Traini, V. Cortellessa, D. D. Pompeo, M. Tucci, ``Towards effective assessment of steady state performance in Java software: Are we there yet?,'' Empirical Software Engineering 28.1, 2023.
\end{thebibliography}


\end{document}
